A Spatial AR System for Axis-aligned Augmentation of Planar Scenes in Industrial Settings

### 2021-07-11 paper/elsarticle/elsarticle-template.tex
paper

We propose a spatial AR system that produces the effect of keystone correction analytically, and that facilitates placement by enabling intuitively placing the desired augmentations in a manner aligned with the axes of an image of the scene acquired by a camera facing downwards towards the scene plane. Moreover, our system is able to handle a projector equipped with a steerable mirror, enabling factory floor augmentation exceeding the bounds of the projector's own immediate field of view.
\end{abstract}

@@

\paragraph{Camera calibration} The recovery of 2D-3D correspondences in support of camera calibration is carried out by relying on a planar calibration surface to automatically identify correspondences between the 3D points on the calibration surface and their 2D correspondences in the image plane. The classical calibration surface is a chessboard pattern. The 3D corner points of the chessboard are obtained \textit{a priori} in a coordinate system defined in the plane of the chessboard\footnote{E.g., $(0,0,0), (1.5,0,0), (3,0,0), \dots, (9,7.5,0)$ for a chessboard with $7~\times{}~6$ corners, with each square of length and width of 1.5 unit, respectively. Note that the units of the chessboard's 3D points give the units of the camera calibration, and---owing to how our projector calibration relies on the camera calibration---of the projector calibration as well.}, requiring knowledge only of the dimensions of the chessboard pattern and of the length of a side of a chessboard square. The corresponding 2D points are obtained, in the same order, using a specialized algorithm \cite{bradski2000opencv}. A set of calibration images is acquired, each with the calibration pattern visible in a different part of the image plane, and such that the center and all corners and edges of the image plane are covered, the camera's autofocus setting is off, and the camera's zoom factor remain fixed. 2D-3D correspondences are then recovered for each calibration image, and the resulting list is passed on as input to an optimization procedure that relies on bundle adjustment to yield the camera calibration matrix~$\mathtt{K}_\text{cam}$ and the associated lens distortion model coefficients.

\paragraph{Projector calibration} As with camera calibration, projector calibration relies on 2D-3D correspondences, yet we obtain them in this case by projecting a pattern of circles. We rely on an algorithm to detect the circle pattern center points in the circles pattern image in the image plane of the projector \cite{bradski2000opencv}, giving the 2D positions of our 2D-3D correspondences (cf.\ Figure~\ref{fig:2d}(a)). We project the circles pattern image to each of the target locations, and use the camera to acquire a projector calibration image for each. Given a projector calibration image, we detect the circle centers of the \textit{projected} circles pattern (cf.\ Figure~\ref{fig:2d}(b)); given the scene plane (the recovery of which we shall return to in the paragraph that follows) and such a 2D circle center $\mathbf{x}$, its 3D correspondence is obtained by intersecting the back-projection of $\mathbf{x}$ with the scene plane (cf.\ Figure~\ref{fig:3d}). Since the algorithm that yields 2D circle centers does so in a consistent ordering, we thus obtain the 2D-3D correspondences between the projector's image plane and the scene required for projector calibration, yielding the projector calibration matrix~$\mathtt{K}_\text{proj}$.

@@

\begin{figure}
    \centering
    \subfloat[\centering Projecting original image.]{{\includegraphics[height=4.2cm]{images/proj_projim.png}}}
    \qquad
    \subfloat[\centering Projecting our warped image.]{{\includegraphics[height=4.2cm]{images/proj_projim_waped.png}}}
    \caption{Projection from the recovered projector viewpoint (bottom left, black; virtual projector in gray) to the scene plane of the original image and of the warped image. (a) Projecting the original image to the scene plane. (b) After warping the original image according to our plane-induced homography for the given target location, the image is projected in a manner that appears free of perspective distortions, aligned with the axes of the virtual camera, and to have the desired dimensions in the scene plane, expressed in metric units. Note that background in the projected image is shown set to black.}
    \label{fig:warp}
\end{figure}

@@

We evaluate our approach by augmenting 15 locations across the floorspace at the Pilotfabrik\footnote{\url{https://www.pilotfabrik.at/}} of TU Vienna, a collaborative space for research on Industry 4.0 topics situated in Vienna, Austria. We contrast our approach with a baseline approach involving manual keystone correction, by aiming with both approaches to place an image for each location aligned with the principal axes of the floorspace, absent of projective distortions, and with the same dimensions (50~cm~$\times$~31.25~cm). All experiments were carried out by the same experienced technician.

@@

\paragraph{Our approach} We began by carrying out a one-time\footnote{Note that once the camera is calibrated, that calibration can be reused if the camera's intrinsics remain fixed, i.e., no change is made to the zoom factor.} calibration of the camera, acquiring 10 camera calibration images (cf.\ Section~\ref{sec:approach:geometry}) and feeding the images as input to our camera calibration module. Separately, for each of the 15 target locations, we produced a projector calibration image (cf.\ again Section~\ref{sec:approach:geometry}) by projecting the circles pattern image to the location in question using the steerable mirror, placing a checkerboard pattern beside the projected pattern, and acquire the image using the downward-facing camera. We then fed these images alongside the output of the camera calibration module to our projector calibration module. For each of the target locations, the steerable mirror was made to point to that location, the circles pattern image was projected to the scene plane, an image was using the camera, and the location was registered in the MDC-X software as a preset. The output of the projector calibration module is a homography per input projector calibration image (cf.\ Section~\ref{sec:approach:homography}). Next, we warped the images to be projected to the respective locations using their corresponding homography, using a third dedicated custom module. These warped images were finally imported into the MDC-X software and associated with their respective location presets.

>>>>

We propose a spatial AR system for planar scenes that produces the effect of keystone correction analytically, and that facilitates placement by enabling intuitively placing the desired augmentations in a manner aligned with the axes of an image of the scene acquired by a camera facing downwards towards the scene plane. Moreover, our system is able to handle a projector equipped with a steerable mirror, enabling factory floor augmentation exceeding the bounds of the projector's own immediate field of view.
\end{abstract}

@@

\paragraph{Camera calibration} We recover 2D-3D correspondences in support of calibrating the downwards-facing camera is carried out by relying on a planar calibration surface to automatically identify correspondences between the 3D points on the calibration surface and their 2D correspondences in the image plane. The classical calibration surface is a chessboard pattern. The 3D corner points of the chessboard are obtained \textit{a priori} in a coordinate system defined in the plane of the chessboard\footnote{E.g., $(0,0,0), (1.5,0,0), (3,0,0), \dots, (9,7.5,0)$ for a chessboard with $7~\times{}~6$ corners, with each square of length and width of 1.5 unit, respectively. Note that the units of the chessboard's 3D points give the units of the camera calibration, and---owing to how our projector calibration relies on the camera calibration---of the projector calibration as well.}, requiring knowledge only of the dimensions of the chessboard pattern and of the length of a side of a chessboard square. The corresponding 2D points are obtained, in the same order, using a specialized algorithm \cite{bradski2000opencv}. A set of calibration images is acquired, each with the calibration pattern visible in a different part of the image plane, and such that the center and all corners and edges of the image plane are covered, the camera's autofocus setting be off, and the camera's zoom factor remain fixed. 2D-3D correspondences are then recovered for each calibration image, and the resulting list is passed on as input to an optimization procedure that relies on bundle adjustment to yield the camera calibration matrix~$\mathtt{K}_\text{cam}$ and the associated lens distortion model coefficients.

\paragraph{Projector calibration} As with camera calibration, projector calibration relies on 2D-3D correspondences, yet we obtain them in this case by projecting a pattern of circles. We rely on an algorithm to detect the circle pattern center points in the circles pattern image in the image plane of the projector \cite{bradski2000opencv}, giving the 2D positions of our 2D-3D correspondences for calibrating the projector (cf.\ Figure~\ref{fig:2d}(a)). We project the circles pattern image to each of the target locations, and use the camera to acquire a projector calibration image for each. Given a projector calibration image acquired using the downwards-facing camera, we detect the circle centers of the \textit{projected} circles pattern (cf.\ Figure~\ref{fig:2d}(b)); given the scene plane (the recovery of which we shall return to in the paragraph that follows) and such a 2D circle center $\mathbf{x}$, its 3D correspondence is obtained by intersecting the back-projection of $\mathbf{x}$ with the scene plane (cf.\ Figure~\ref{fig:3d}). Since the algorithm that yields 2D circle centers does so in a consistent ordering, we thus obtain the 2D-3D correspondences between the projector's image plane and the scene required for projector calibration, yielding the projector calibration matrix~$\mathtt{K}_\text{proj}$.

@@

\begin{figure}
    \centering
    \subfloat[\centering Projecting original image.]{{\includegraphics[height=4.2cm]{images/proj_projim.png}}}
    \qquad
    \subfloat[\centering Projecting our warped image.]{{\includegraphics[height=4.2cm]{images/proj_projim_waped.png}}}
    \caption{Projection from the recovered projector viewpoint (bottom left, black; virtual projector in center, gray) to the scene plane of the original image and of the warped image. (a) Projecting the original image to the scene plane. (b) After warping the original image according to our plane-induced homography for the given target location, the image is projected in a manner that appears free of perspective distortions, aligned with the axes of the virtual camera (via the virtual projector), and to have the desired dimensions in the scene plane, expressed in metric units. Note that background in the projected image is shown set to black.}
    \label{fig:warp}
\end{figure}

@@

We evaluate our approach by augmenting 15 locations across the floorspace at the Pilotfabrik\footnote{\url{https://www.pilotfabrik.at/}} of TU Vienna, a collaborative space for research on Industry 4.0 topics situated in Vienna, Austria. We contrast our approach with a baseline approach involving manual keystone correction, by aiming with both approaches to place an image for each location aligned with the principal axes of the floorspace, absent of projective distortions, and with the same dimensions (50~cm~$\times$~31.25~cm\footnote{}). All experiments were carried out by the same experienced technician.

@@

\paragraph{Our approach} We began by carrying out a one-time\footnote{Note that once the camera is calibrated, that calibration can be reused if the camera's intrinsics remain fixed, e.g., no change is made to the zoom factor.} calibration of the camera, acquiring 10 camera calibration images (cf.\ Section~\ref{sec:approach:geometry}) and feeding the images as input to our camera calibration module. Separately, for each of the 15 target locations, we produced a projector calibration image (cf.\ again Section~\ref{sec:approach:geometry}) by projecting the circles pattern image to the location in question using the steerable mirror, placing a checkerboard pattern beside the projected pattern, and acquire the image using the downward-facing camera. We then fed these images alongside the output of the camera calibration module to our projector calibration module. For each of the target locations, the steerable mirror was made to point to that location, the circles pattern image was projected to the scene plane, an image was using the camera, and the location was registered in the MDC-X software as a preset. The output of the projector calibration module is a homography per input projector calibration image (cf.\ Section~\ref{sec:approach:homography}). Next, we warped the images to be projected to the respective locations using their corresponding homography, using a third dedicated custom module. These warped images were finally imported into the MDC-X software and associated with their respective location presets.
